Technical Report

### 2018-06-06 fully-abstract-comp/technical-report.tex
Typos

\begin{lemma}[Combined independent heap memory satisfies disjoint world]
  \label{sec:combined-memory-disjoint-world}
  If $\memSatHeap{\overline{\sigma_1},ms_{S,1},\ms_{T,1}}{W_1}$ and $\memSatHeap{\overline{\sigma_2},ms_{S,2},\ms_{T,2}}{W_2}$, then $\memSatHeap{\overline{\sigma_1}\uplus\overline{\sigma_2},ms_{S,1}\uplus \ms_{S,2},\ms_{T,1}\uplus \ms_{T,2}}{W_1 \uplus W_2}$.
\end{lemma}
\begin{proof}
  Unfolding the definitions, it's easy to construct the memory and seal partitions $R_{\ms,3}$ and $R_{\var{seal},3}$ from the corresponding partitions of the separate memories.
  Constructing $R_{W,3}$ from $R_{W,1}$ and $R_{w,2}$ is a bit harder, but we can use Lemmas~\ref{lem:oplus-distr-uplus},~\ref{lem:purePart-duplicable},~\ref{lem:uplus-assoc-comm} and~\ref{lem:oplus-assoc-comm} to manipulate the world equalities as follows:
  \begin{align*}
    W_1 \uplus W_2 &= (\purePart{W_1} \oplus W_1) \uplus (W_2 \oplus \purePart{W_2})\\
                   &= (\purePart{W_1} \uplus W_2) \oplus (W_1 \uplus \purePart{W_2})\\
                   &= (\purePart{W_1} \uplus \bigoplus_r R_{W,2}(r)) \oplus ((\bigoplus_r R_{W,1}(r)) \uplus \purePart{W_2})\\
                   &= \bigoplus_r (\purePart{W_1} \uplus R_{W,2}(r)) \oplus \bigoplus_r (R_{W,1}(r) \uplus \purePart{W_2})
  \end{align*}
  We can then define
  \begin{equation*}
    R_{W,3}(r) =
    \begin{cases}
      \purePart(W_1) \uplus R_{W,2}(r) &\text{when } r \in \dom(R_{W,2})\\
      \purePart(W_2) \uplus R_{W,1}(r) &\text{when } r \in \dom(R_{W,1})
    \end{cases}
  \end{equation*}
  Lemma~\ref{lem:uplus-future} and the monotonicity of the regions' memory predicates then yield the required results.
\end{proof}

@@

\[
  \readCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      \qquad \forall r \in S \ldotp \pwheap(r) \nsubsim \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \forall r \in S \ldotp |R(r)| = 1\\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \forall r \in S \ldotp \pwfree(r) \nsubsim \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwfree} \ldotp \\
      \quad \exists M : S \fun \powerset{\MemSeg} \\
      \qquad \biguplus_{r\in S} \dom(M(r)) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      % \qquad \biguplus_{r\in S} R(r) \# \biguplus_{r\in S} C(r) \wedge \\
      \qquad \forall r \in S \ldotp  \pwheap(r) \nsim \codereg{\_,\_,M(r),\gc}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions.}
\lau{TODO: allow code regions to be merged into one. Allow for (... forgot to write the rest, but probably related to splicing regions.) }

@@

\begin{lemma}[Code region for untrusted components stronger than standard safe memory region]
  \label{lem:codereg-untrusted-stdreg}
  If
  \begin{itemize}
  \item $\emptyset\neq\dom(\mscode) \mathrel{\#} \ta$
  \end{itemize}
  then $\codereg{\sigrets,\sigcloss,\mscode,\gc} \nsubsim \stdreg{\dom(\mscode),\gc}{\pur}$ 
\end{lemma}
\begin{proof}
  Take $\hat{W}$, then we need to prove that
  \begin{equation*}
    H^\mathrm{code}\ ;\sigrets\;\sigcloss\;\mscode\;\gc \; \hat{W} \nsubsim H_{\dom(\mscode)}^{\mathrm{std},\square}\;\hat{W}
  \end{equation*}
  So take $\npair{\ms_S,\ms_T} \in H^\mathrm{code}\ ;\sigrets\;\sigcloss\;\mscode\;\gc \; \hat{W}$, then we know that
  \begin{itemize}
  \item $\ms_S = \ms_T = \mscode$ 
  \item $\dom(\mscode) =[\aaddr,\baddr]$
  \item $\dom(\mscode) \subseteq \ta \vee (\dom(\mscode)\mathrel{\#} \ta \wedge \sigrets = \emptyset)$, but we know that $\emptyset \neq\dom(\mscode) \mathrel{\#} \ta$, so we get that $\sigrets = \emptyset$.
  \item For all $a \in \dom(\code)$, $n'<n$, $\npair[n']{(\code(a),\code(a))} \in \lrv(\purePart{\xi(\hat{W})})$
  \end{itemize}

@@

\begin{lemma}[Code memory for untrusted components safely readable]
  \label{lem:code-memory-untrusted-readable}
  If
  \begin{itemize}
  \item $\dom(\mscode) \mathrel{\#} \ta$
  \item $\pwheap(r_{\mathrm{code}}) = \codereg{\sigrets,\sigcloss,\mscode,\gc}$
  \item $A \subseteq \dom(\mscode)$,
  \end{itemize}
  we have that $\npair{A} \in \readCond{\normal,W}$.
\end{lemma}
\begin{proof}
  Follows by defintion of $\readCond$ from Lemma~\ref{lem:codereg-untrusted-stdreg}.
\end{proof}

>>>>

\begin{lemma}[Combined independent heap memory satisfies disjoint world]
  \label{sec:combined-memory-disjoint-world}
  If $\memSatHeap{\overline{\sigma_1},ms_{S,1},\ms_{T,1}}{W_1}$ and $\memSatHeap{\overline{\sigma_2},ms_{S,2},\ms_{T,2}}{W_2}$, then $\memSatHeap{\overline{\sigma_1}\uplus\overline{\sigma_2},ms_{S,1}\uplus \ms_{S,2},\ms_{T,1}\uplus \ms_{T,2}}{W_1 \uplus W_2}$.
\end{lemma}
\begin{proof}
  Unfolding the definitions, it's easy to construct the memory and seal partitions $R_{\ms,3}$ and $R_{\var{seal},3}$ from the corresponding partitions of the separate memories.
  Constructing $R_{W,3}$ from $R_{W,1}$ and $R_{w,2}$ is a bit harder, but we can use Lemmas~\ref{lem:oplus-distr-uplus},~\ref{lem:purePart-duplicable},~\ref{lem:uplus-assoc-comm} and~\ref{lem:oplus-assoc-comm} to manipulate the world equalities as follows:
  \begin{align*}
    W_1 \uplus W_2 &= (\purePart{W_1} \oplus W_1) \uplus (W_2 \oplus \purePart{W_2})\\
                   &= (\purePart{W_1} \uplus W_2) \oplus (W_1 \uplus \purePart{W_2})\\
                   &= (\purePart{W_1} \uplus \bigoplus_r R_{W,2}(r)) \oplus ((\bigoplus_r R_{W,1}(r)) \uplus \purePart{W_2})\\
                   &= \bigoplus_r (\purePart{W_1} \uplus R_{W,2}(r)) \oplus \bigoplus_r (R_{W,1}(r) \uplus \purePart{W_2})
  \end{align*}
  We can then define
  \begin{equation*}
    R_{W,3}(r) =
    \begin{cases}
      \purePart{W_1} \uplus R_{W,2}(r) &\text{when } r \in \dom(R_{W,2})\\
      \purePart{W_2} \uplus R_{W,1}(r) &\text{when } r \in \dom(R_{W,1})
    \end{cases}
  \end{equation*}
  Lemma~\ref{lem:uplus-future} and the monotonicity of the regions' memory predicates then yield the required results.
\end{proof}

@@

\[
  \readCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      \qquad \forall r \in S \ldotp \pwheap(r) \nsubsim \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions. Check whether needed for the stack condition.}
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \stackReadCond{W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\linear, \pwfree} \ldotp \\
      \quad \exists R : S \fun \powerset{\nats} \\
      \qquad \forall r \in S \ldotp |R(r)| = 1\\
      \qquad \biguplus_{r\in S} R(r) \supseteq A \wedge \\
      \qquad \forall r \in S \ldotp \pwfree(r) \nsubsim \stdreg{R(r),\gc}{\pur}
    \end{array}
  \right\}
\]
where $\iota_A$ is a standard region defined in Section~\ref{sec:standard-regions}.
\[
  \xReadCond{\lin,W} = \left\{ \npair{A} \middle| 
    \begin{array}{l}
      \exists S \subseteq \addressable{\lin, \pwheap} \ldotp \\
      \quad \exists M : S \fun \powerset{\MemSeg} \\
      \qquad \biguplus_{r\in S} \dom(M(r)) \supseteq A \wedge\\
      \qquad (\lin = \linear \Rightarrow \forall r\ldotp |R(r)|  = 1) \wedge\\
      % \qquad \biguplus_{r\in S} R(r) \# \biguplus_{r\in S} C(r) \wedge \\
      \qquad \forall r \in S \ldotp  \pwheap(r) \nsim \codereg{\_,\_,M(r),\gc}
    \end{array}
  \right\}
\]
\lau{RESOLVED: Make this condition require a set of adjacent regions.}
\lau{TODO: allow code regions to be merged into one. Allow for (... forgot to write the rest, but probably related to splicing regions.) }

@@

\begin{lemma}[Code region for untrusted components stronger than standard safe memory region]
  \label{lem:codereg-untrusted-stdreg}
  If
  \begin{itemize}
  \item $\emptyset\neq\dom(\mscode) \mathrel{\#} \ta$
  \end{itemize}
  then $\codereg{\sigrets,\sigcloss,\mscode,\gc} \nsubsim \stdreg{\dom(\mscode),\gc}{\pur}$ 
\end{lemma}
\begin{proof}
  Take $\hat{W}$, then we need to prove that
  \begin{equation*}
    H^\mathrm{code}\;\sigrets\;\sigcloss\;\mscode\;\gc \; \hat{W} \nsubsim H_{\dom(\mscode)}^{\mathrm{std},\square}\;\hat{W}
  \end{equation*}
  So take $\npair{\ms_S,\ms_T} \in H^\mathrm{code}\;\sigrets\;\sigcloss\;\mscode\;\gc \; \hat{W}$, then we know that
  \begin{itemize}
  \item $\ms_S = \ms_T = \mscode$ 
  \item $\dom(\mscode) =[\aaddr,\baddr]$
  \item $\dom(\mscode) \subseteq \ta \vee (\dom(\mscode)\mathrel{\#} \ta \wedge \sigrets = \emptyset)$, but we know that $\emptyset \neq\dom(\mscode) \mathrel{\#} \ta$, so we get that $\sigrets = \emptyset$.
  \item For all $a \in \dom(\code)$, $n'<n$, $\npair[n']{(\code(a),\code(a))} \in \lrv(\purePart{\xi(\hat{W})})$
  \end{itemize}

@@

\begin{lemma}[Code memory for untrusted components safely readable]
  \label{lem:code-memory-untrusted-readable}
  If
  \begin{itemize}
  \item $\dom(\mscode) \mathrel{\#} \ta$
  \item $\pwheap(r_{\mathrm{code}}) = \codereg{\sigrets,\sigcloss,\mscode,\gc}$
  \item $A \subseteq \dom(\mscode)$,
  \end{itemize}
  we have that $\npair{A} \in \readCond{\normal,W}$.
\end{lemma}
\begin{proof}
  Follows by defintion of $\readCond{}$ from Lemma~\ref{lem:codereg-untrusted-stdreg}.
\end{proof}
